---
title: "Regression"
student: "Isabelle Kirby", "Bridgette Bryant" 
NetID: "IRK180000", "BMB180001"
Assignment: "Linear Models"
Date: "09/16/2021"
---
This is the data I have chosen to use for this assignment. It basically compiles
information on the overall air quality of different cities over time.

It has 32191 observations initially.
```{r}
df <- read.csv("Air_Pollution.csv")
str(df)
```
I then take out the instances that have incomplete information.
```{r}
df <- df[(complete.cases(df)),]
str(df)
```

Now I'm creating the training and testing sets.
```{r}
i <-sample(1:nrow(df), .8*nrow(df), replace=FALSE)
train <- df[i,]
test <- df[-i,]
```

Plotting the linear regression
```{r}
lm1 <- lm(NO2~NO2.temporal.coverage, data=train)
summary(lm1)
plot(lm1)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
