---
title: "Kernel and Ensemble Methods: Classification"
author: "Isabelle Kirby, Bridgette Bryant"
output:
  pdf_document: default
  html_document: default
---

# SVM Classification for Korea's top high elo teams in League of Legends

<bleh> 


## Cleaning Data

First we have to unzip the archive (they are large data sets nearly 100k games). Then we will save the


```{r}

win_stats_df <- read.csv((unz("League_Data/league_korea_high_elo_team_stats.zip", "win_team_stats.csv")))
lose_stats_df <- read.csv((unz("League_Data/league_korea_high_elo_team_stats.zip", "lose_team_stats.csv")))

str(win_stats_df)
str(lose_stats_df)

```

Now we will merge the two data sets together based on their matching gameId column. This way our model can catagorize our data by team 0 or team 1 winning based on both teams contrasting stats.
```{r}
# Replacing column names for rbind
colnames(win_stats_df) <- c('kill1', 'kill2', 'kill3', 'kill4', 'kill5', 'death1', 'death2', 'death3', 'death4', 'death5', 'totalDamageDealtToChampions1', 'totalDamageDealtToChampions2', 'totalDamageDealtToChampions3', 'totalDamageDealtToChampions4', 'totalDamageDealtToChampions5', 'goldEarned1', 'goldEarned2', 'goldEarned3', 'goldEarned4', 'goldEarned5', 'visionScore1', 'visionScore2', 'visionScore3', 'visionScore4', 'visionScore5', 'totalTimeCrowdControlDealt1', 'totalTimeCrowdControlDealt2', 'totalTimeCrowdControlDealt3', 'totalTimeCrowdControlDealt4', 'totalTimeCrowdControlDealt5', 'gameId')
colnames(lose_stats_df) <- c('kill1', 'kill2', 'kill3', 'kill4', 'kill5', 'death1', 'death2', 'death3', 'death4', 'death5', 'totalDamageDealtToChampions1', 'totalDamageDealtToChampions2', 'totalDamageDealtToChampions3', 'totalDamageDealtToChampions4', 'totalDamageDealtToChampions5', 'goldEarned1', 'goldEarned2', 'goldEarned3', 'goldEarned4', 'goldEarned5', 'visionScore1', 'visionScore2', 'visionScore3', 'visionScore4', 'visionScore5', 'totalTimeCrowdControlDealt1', 'totalTimeCrowdControlDealt2', 'totalTimeCrowdControlDealt3', 'totalTimeCrowdControlDealt4', 'totalTimeCrowdControlDealt5', 'gameId')

# Adding column based on dataset it is in
library(dplyr)

win_stats_df <- win_stats_df %>%
  mutate(won="True")

lose_stats_df <- lose_stats_df %>%
  mutate(won ="False")

#full_stats_df <- merge(win_stats_df, lose_stats_df, by = "gameId")
full_stats_df <- rbind(win_stats_df, lose_stats_df)
drop <- c("gameId")
full_stats_df <- full_stats_df[,!(names(full_stats_df) %in% drop)]

# Make our won column a factor for classification
full_stats_df$won <- as.factor(full_stats_df$won)

str(full_stats_df)
```
```{r}
i <- sample(1:nrow(full_stats_df), .2*nrow(full_stats_df), replace=FALSE)
full_stats_smol <- full_stats_df[i,]

lolDataless <- full_stats_smol %>% rowwise() %>% mutate(TotalKill = sum(c_across(kill1:kill5)))

lolDataless <- lolDataless %>% rowwise() %>% mutate(TotalDeath = sum(c_across(death1:death5)))

lolDataless <- lolDataless %>% rowwise() %>% mutate(TotalDamage = sum(c_across(totalDamageDealtToChampions1:totalDamageDealtToChampions5)))

lolDataless <- lolDataless %>% rowwise() %>% mutate(TotalGold = sum(c_across(goldEarned1:goldEarned5)))

lolDataless <- lolDataless %>% rowwise() %>% mutate(TotalVision = sum(c_across(visionScore1:visionScore5)))

lolDataless <- lolDataless %>% rowwise() %>% mutate(TotalCrowdControl = sum(c_across(totalTimeCrowdControlDealt1:totalTimeCrowdControlDealt5)))

drop <- c('kill1', 'kill2', 'kill3', 'kill4', 'kill5', 'death1', 'death2', 'death3', 'death4', 'death5', 'totalDamageDealtToChampions1', 'totalDamageDealtToChampions2', 'totalDamageDealtToChampions3', 'totalDamageDealtToChampions4', 'totalDamageDealtToChampions5', 'goldEarned1', 'goldEarned2', 'goldEarned3', 'goldEarned4', 'goldEarned5', 'visionScore1', 'visionScore2', 'visionScore3', 'visionScore4', 'visionScore5', 'totalTimeCrowdControlDealt1', 'totalTimeCrowdControlDealt2', 'totalTimeCrowdControlDealt3', 'totalTimeCrowdControlDealt4', 'totalTimeCrowdControlDealt5')

lolDataless = lolDataless[, !(names(lolDataless) %in% drop)]
summary(lolDataless)
```

Next let's randomly divide the data into train, test, and validate:

```{r}
set.seed(1010)
i <- sample(1:nrow(lolDataless), 0.75*nrow(lolDataless), replace=FALSE)
full_stats_train <- lolDataless[i,]
full_stats_test <- lolDataless[-i,]

summary(full_stats_train)
```


## Data Exploration

Next we will plot some of our data to see possible differences/correlations. Time to do some data exploration.

```{r}
boxplot(full_stats_train$won, full_stats_train$TotalDeath, main="Won and Deaths", xlab="Won", ylab="Total Deaths", outline = FALSE, col = 'aquamarine')

boxplot(full_stats_train$won, full_stats_train$TotalKill, main="Won and kills", xlab="Won", ylab="Total kills", outline = FALSE, col = 'azure')

boxplot(full_stats_train$won, full_stats_train$TotalGold, main="Won and Gold Earned", xlab="Won", ylab="Total Gold Earned", outline = FALSE, col = 'beige')

boxplot(full_stats_train$won, full_stats_train$TotalVision, main="Won and Vision Score", xlab="Won", ylab="Total Vision Score", outline = FALSE, col = 'bisque')

boxplot(full_stats_train$won, full_stats_train$TotalCrowdControl, main="Won and totalTimeCrowdControlDealt", xlab="Won", ylab="Total totalTimeCrowdControlDealt", outline = FALSE, col='red')

plot(full_stats_train$TotalKill, full_stats_train$TotalGold, main="Kills and Gold Earned", xlab="Kills", ylab="Total Gold Earned", col = rep(1:6))

plot(full_stats_train$TotalDeath, full_stats_train$TotalDeath, main="Deaths and Gold Earned", xlab="Deaths", ylab="Total Gold Earned", col = rep(6:12))

plot(full_stats_train$TotalVision, full_stats_train$TotalGold, main="Vision Score and Gold Earned", xlab="Vision Score", ylab="Total Gold Earned", col = rep(12:18))

plot(full_stats_train$TotalCrowdControl, full_stats_train$TotalGold, main="totalTimeCrowdControlDealt and Gold Earned", xlab="totalTimeCrowdControlDealt", ylab="Total Gold Earned", col = rep(18:24))

```

## SVM Classification

### Linear

#### Training

Now we will build our logistic regression model
```{r}
library(e1071)
svm_lin <- svm(won~., data=full_stats_train, kernel="linear", cost=10, scale=TRUE)
summary(svm_lin)
```

#### Testing & Evaluation

Now we can evaluate on the test set:

```{r}
library(caret)
svm_probs_lin <- predict(svm_lin, newdata = full_stats_test)

confusionMatrix(svm_probs_lin, reference = full_stats_test$won)
plot(svm_lin, full_stats_test, TotalGold ~ TotalVision)
plot(svm_lin, full_stats_test, TotalGold ~ TotalDeath)
plot(svm_lin, full_stats_test, TotalKill ~ TotalDeath)
plot(svm_lin, full_stats_test, TotalKill ~ TotalVision)
plot(svm_lin, full_stats_test, TotalKill ~ TotalCrowdControl)
plot(svm_lin, full_stats_test, TotalKill ~ TotalDamage)
```

### Polynomial

#### Training

Now we will build our logistic regression model
```{r}
library(e1071)
svm_poly <- svm(won~., data=full_stats_train, kernel="polynomial", cost=10, scale=TRUE)
summary(svm_poly)
```

#### Testing & Evaluation

Now we can evaluate on the test set:

```{r}
library(caret)
svm_probs_poly <- predict(svm_poly, newdata = full_stats_test)

confusionMatrix(svm_probs_poly, reference = full_stats_test$won)
plot(svm_poly, full_stats_test, TotalGold ~ TotalVision)
plot(svm_poly, full_stats_test, TotalGold ~ TotalDeath)
plot(svm_poly, full_stats_test, TotalKill ~ TotalDeath)
plot(svm_poly, full_stats_test, TotalKill ~ TotalVision)
plot(svm_poly, full_stats_test, TotalKill ~ TotalCrowdControl)
plot(svm_poly, full_stats_test, TotalKill ~ TotalDamage)
```

### Radial

#### Training

Now we will build our logistic regression model
```{r}
library(e1071)
svm_rad <- svm(won~., data=full_stats_train, kernel="radial", cost=10, scale=TRUE)
summary(svm_rad)
```

#### Testing & Evaluation

Now we can evaluate on the test set:

```{r}
library(caret)
svm_probs_rad <- predict(svm_rad, newdata = full_stats_test)

confusionMatrix(svm_probs_rad, reference = full_stats_test$won)
plot(svm_rad, full_stats_test, TotalGold ~ TotalVision)
plot(svm_rad, full_stats_test, TotalGold ~ TotalDeath)
plot(svm_rad, full_stats_test, TotalKill ~ TotalDeath)
plot(svm_rad, full_stats_test, TotalKill ~ TotalVision)
plot(svm_rad, full_stats_test, TotalKill ~ TotalCrowdControl)
plot(svm_rad, full_stats_test, TotalKill ~ TotalDamage)
```

## SVM Linear vs Polynomial vs Radial
Analyzing the results of each model based on the algorithms.

### SVM Linear

<bleh>

### SVM Polynomial

<bleh>

### SVM Radial

<bleh>